---
output: 
  html_document: 
    toc: yes
    toc_depth: 4
    toc_float: yes
---


# 20211009_10x_LY sc10x               

only ILC2 selected            
(without the upper left CC part)                
(which could be mixed with other celltypes like stromal)          


```{r message=FALSE, warning=FALSE}
source("../../../analysis.10x.r")
```

## subset ILC2          

### processed obj           

```{r}
GEX.seur.raw <- readRDS("../analysis_1101/sc10x.GEX.seur.pre1105.rds")
GEX.seur.raw
```

```{r fig.width=12,fig.height=4.5}
DimPlot(GEX.seur.raw, reduction = "umap", group.by = "seurat_clusters",label = T, repel = F, label.size = 3.5) +
  DimPlot(GEX.seur.raw, reduction = "umap", group.by = "preAnno_2",label = T, repel = F, label.size = 3.2)
```

only cluster_1,3,4,5 selected              

```{r fig.width=12,fig.height=4.5}
DimPlot(GEX.seur.raw, reduction = "umap", group.by = "seurat_clusters",label = T, repel = F, label.size = 3.5) +
  FeaturePlot(GEX.seur.raw, reduction = "umap", features = "percent.mt")
```

#### check some cutoffs          

if could exclude those little group of ILC2 cells with high mito and low nFeature             

```{r fig.width=12,fig.height=4.5}
DimPlot(GEX.seur.raw, reduction = "umap", group.by = "seurat_clusters",label = T, repel = F, label.size = 3.5) +
  FeaturePlot(subset(GEX.seur.raw, subset=percent.mt <7.5)
              , reduction = "umap", features = "percent.mt")
```

```{r fig.width=12,fig.height=4.5}
FeaturePlot(GEX.seur.raw, reduction = "umap", features = c("nFeature_RNA","nCount_RNA"))
```

```{r fig.width=12,fig.height=4.5}
FeaturePlot(subset(GEX.seur.raw, subset= nCount_RNA < 25000 & nFeature_RNA < 4500 & nFeature_RNA > 1000 & percent.mt < 7.5), 
            reduction = "umap", features = c("nFeature_RNA","nCount_RNA"))
```

### only ILC2          

```{r}
GEX.seur <- subset(GEX.seur.raw, subset = seurat_clusters %in% c(1,3,4,5))
GEX.seur <- subset(GEX.seur, subset= nCount_RNA < 16000 & nFeature_RNA < 3600 & nFeature_RNA > 1000 & percent.mt < 7.5)
GEX.seur <- subset(GEX.seur, features = rownames(GEX.seur)[rowSums(GEX.seur@assays[['RNA']]@data > 0)>=3])
GEX.seur
```

```{r}
quantile(GEX.seur$nFeature_RNA,prob=seq(0,1,0.025))
```

         
```{r fig.width=12,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", group.by = "preAnno_1",label = F, repel = F, label.size = 3.5) +
  DimPlot(GEX.seur, reduction = "umap", group.by = "preAnno_2",label = F, repel = F, label.size = 3.2)
```

#### check the data        

```{r fig.width=12,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", group.by = "DoubletFinder0.1",label = F, repel = F, label.size = 3.5) +
  FeaturePlot(GEX.seur, reduction = "umap", features = "percent.mt")
```

```{r fig.width=10,fig.height=4}
plota <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.mt", group.by = "orig.ident") + 
             coord_cartesian(xlim =c(0, 30000), ylim = c(0, 10))
plotb <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "nFeature_RNA", group.by = "orig.ident") + 
             coord_cartesian(xlim =c(0, 30000), ylim = c(0, 5000))
plota + plotb
```
```{r fig.width=12,fig.height=4.5}
FeaturePlot(GEX.seur, reduction = "umap", features = c("nFeature_RNA","nCount_RNA"))
```

```{r fig.width=12,fig.height=4.5}
FeaturePlot(subset(GEX.seur, subset= nCount_RNA < 16000 & nFeature_RNA < 3200 & nFeature_RNA > 1000 & percent.mt < 7.5), 
            reduction = "umap", features = c("nFeature_RNA","nCount_RNA"))
```
```{r}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, pt.size = 0.1, group.by = "SP.info")
```

```{r}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, pt.size = 0.1, group.by = "FB.info")
```

```{r fig.width=12,fig.height=6}
DimPlot(GEX.seur, group.by = "FB.info", split.by = "FB.info", ncol = 4,
        cols = c("#05BE78","#5ECDF2","#739BDD","#B7E16F","#87C0C9","#7756FA","#9855B9","#6F9920"))
```

```{r fig.width=12.6,fig.height=4.5}
DimPlot(GEX.seur, group.by = "SP.info", split.by = "SP.info", ncol = 3)
```

```{r fig.height=20, fig.width=12}
genes_to_check <- c("Fcer1g","Klrb1c","Ncr1","Il22",
                    "Ccr6","Tbx21","Ifng","Eomes",
                    "Gata3","Il1rl1","Il13","Il17a",
                    "Il4","Il5","Klrg1","Rorc",
                    "Il7r","Thy1","Kdm6b","Ptprc",
                    "Cd3d","Cd3g","Cd4",
                    #"Cd8a",
                    "Trac","Trdc","Epcam","Pecam1","Siglech",
                    "Hist1h1b","Top2a","Mcm6","Mki67")

FeaturePlot(GEX.seur, features = genes_to_check, ncol = 4)
```

## re-clustering         

```{r paged.print=FALSE}
# remove unwanted metadata
GEX.seur@meta.data <- GEX.seur@meta.data[,c(1:8,12,14,15:17)]
head(GEX.seur@meta.data)
```

```{r fig.width= 8, fig.height=3.2}
plota <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "percent.mt", group.by = "orig.ident")  + 
             coord_cartesian(xlim =c(0, 20000), ylim = c(0, 10))
plotb <- FeatureScatter(GEX.seur, feature1 = "nCount_RNA", feature2 = "nFeature_RNA", group.by = "orig.ident") + 
             coord_cartesian(xlim =c(0, 20000), ylim = c(0, 4000))
plota + plotb
```

```{r fig.width=7,fig.height=4}
sl_stat <- table(GEX.seur$FB.info)
barplot(sl_stat,ylim = c(0,2200),col = c("#05BE78","#5ECDF2","#739BDD","#B7E16F","#87C0C9","#7756FA","#9855B9","#6F9920"),
        main = "Feature Barcode statistics, only ILC2",cex.names = 0.75)
text(x=1:10*1.2-0.45,y=sl_stat+125,paste0(sl_stat,"\n",100*round(as.numeric(sl_stat/sum(sl_stat)),4),"%"),cex = 0.75)
```

```{r fig.height=6, message=FALSE, warning=FALSE, fig.width=15}
GEX.seur <- FindVariableFeatures(GEX.seur, selection.method = "vst", nfeatures = 800)

# Identify the 10 most highly variable genes
#top10 <- head(VariableFeatures(GEX.seur), 10)
top40 <- head(VariableFeatures(GEX.seur), 40)

# plot variable features with and without labels
plot1 <- VariableFeaturePlot(GEX.seur)
plot2 <- LabelPoints(plot = plot1, points = top40, repel = T)
plot1 + plot2
```
```{r}
top40
```

```{r}
GEX.seur <- ScaleData(GEX.seur, features = rownames(GEX.seur))
```
### PCA       

```{r}
# exclude MT genes  
MT_gene <- grep("^mt-",rownames(GEX.seur),value = T)
Ribo_gene <- grep("^Rpl|^Rps", rownames(GEX.seur),value = T)
GEX.seur <- RunPCA(GEX.seur, features = setdiff(VariableFeatures(object = GEX.seur),c(MT_gene,Ribo_gene)))
```

```{r fig.width=8.2, fig.height=3.2}
DimPlot(GEX.seur, reduction = "pca",dims = 1:2, group.by = "preAnno_1") +
  DimPlot(GEX.seur, reduction = "pca",dims = 3:4, group.by = "preAnno_1")
```

```{r fig.width=8.2, fig.height=3.2}
DimPlot(GEX.seur, reduction = "pca",dims = 1:2, group.by = "preAnno_2") +
  DimPlot(GEX.seur, reduction = "pca",dims = 3:4, group.by = "preAnno_2")
```


```{r pcsheat,fig.width=9,fig.height=12}
DimHeatmap(GEX.seur, dims = 1:24, cells = 1500, balanced = TRUE,ncol = 4)
```


##### decide PCs to use          
     
```{r}
ElbowPlot(GEX.seur,ndims = 24)
```
would take PCs 1-15 for next  

```{r}
PCs <- 1:15
GEX.seur <- FindNeighbors(GEX.seur, dims = PCs,k.param = 80)
GEX.seur <- FindClusters(GEX.seur,  resolution = 0.6, method = 'igraph')
```

### tsne/umap            


```{r}
#GEX.seur <- RunTSNE(GEX.seur, dims=PCs, max_iter = 2000)   
#GEX.seur <- RunUMAP(GEX.seur, dims=PCs, n.neighbors = 80) 
```

```{r eval=FALSE, include=FALSE}
saveRDS(GEX.seur, "adv_1110.GEX.seur_ILC2.afterTSNE.rds")
```

```{r include=FALSE}
GEX.seur <- readRDS("adv_1110.GEX.seur_ILC2.afterTSNE.rds")
```

```{r eval=FALSE, include=FALSE, paged.print=FALSE}
head(GEX.seur@meta.data)
```


```{r fig.width=9.2,fig.height=3.2}
DimPlot(GEX.seur, reduction = "tsne", label = T) + DimPlot(GEX.seur, reduction = "umap", label = T)
```


### check the data        

```{r fig.width=12,fig.height=4.5}
DimPlot(GEX.seur, reduction = "umap", group.by = "DoubletFinder0.1",label = F, repel = F, label.size = 3.5) +
  FeaturePlot(GEX.seur, reduction = "umap", features = "percent.mt")
```

```{r fig.width=12,fig.height=4.5}
FeaturePlot(GEX.seur, reduction = "umap", features = c("nFeature_RNA","nCount_RNA"))
```

```{r}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, pt.size = 0.1, group.by = "SP.info")
```

```{r}
VlnPlot(GEX.seur, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, pt.size = 0.1, group.by = "FB.info")
```

```{r fig.width=12,fig.height=5.2}
DimPlot(GEX.seur, group.by = "FB.info", split.by = "FB.info", ncol = 4,
        cols = c("#05BE78","#5ECDF2","#739BDD","#B7E16F","#87C0C9","#7756FA","#9855B9","#6F9920"))
```

```{r fig.width=12,fig.height=3.6}
DimPlot(GEX.seur, group.by = "SP.info", split.by = "SP.info", ncol = 3)
```

### check markers           

```{r fig.width=4.8, fig.height=5.6}
DotPlot(GEX.seur, features = genes_to_check[genes_to_check %in% rownames(GEX.seur)],
             assay='RNA' , group.by = "seurat_clusters" )  + coord_flip()
```

```{r fig.height=18, fig.width=12}
genes_to_check <- c("Fcer1g","Klrb1c","Ncr1","Il22",
                    "Ccr6","Tbx21","Ifng","Eomes",
                    "Gata3","Il1rl1","Il13","Il17a",
                    "Il4","Il5","Klrg1","Rorc",
                    "Il7r","Thy1","Kdm6b","Ptprc",
                    "Cd3d","Cd3g","Cd4",
                    #"Cd8a",
                    "Trac","Trdc","Epcam","Pecam1","Siglech",
                    "Hist1h1b","Top2a","Mcm6","Mki67")

FeaturePlot(GEX.seur, features = genes_to_check, ncol = 4)
```


```{r fig.width=4.5, fig.height=3.6}
# 
genes_nature2017 <- c("Tbx21","Ifng","Ccl5","Il12rb1",
                      "Gata3","Il1rl1","Il5","Il13",
                      "Rorc","Il17a","Ahr","Il23r")

DotPlot(GEX.seur, features = genes_nature2017[genes_nature2017 %in% rownames(GEX.seur)],
             assay='RNA' , group.by = "seurat_clusters" )  + coord_flip()
```

```{r fig.height=6.75, fig.width=12}
FeaturePlot(GEX.seur, features = genes_nature2017, ncol = 4)
```

### find markers                      

```{r message=FALSE, warning=FALSE, paged.print=TRUE}
# find markers for every cluster compared to all remaining cells, report only the positive ones
#GEX.markers.ILC2_adv <- FindAllMarkers(GEX.seur, only.pos = TRUE, min.pct = 0.1, logfc.threshold = 0.1,
#                                  test.use = "MAST")
GEX.markers.ILC2_adv <- read.table("GEX.markers.ILC2_adv.1110.csv", header = TRUE, sep = ",")

markers.top16 <- GEX.markers.ILC2_adv %>% group_by(cluster) %>% filter(avg_log2FC>0.25)  %>% top_n(n = 16, wt = avg_log2FC)
markers.top16

#GEX.markers.ILC2_pre %>% group_by(cluster) %>% filter(pct.1 > 0.2 & pct.2 <0.1) %>% top_n(n = 8, wt = avg_log2FC)
#GEX.markers.ILC2_pre %>% group_by(cluster) %>% top_n(n = 80, wt = avg_log2FC) %>% filter(gene %in% c("Top2a","Mki67") )
```

```{r eval=FALSE, include=FALSE}
write.table(GEX.markers.ILC2_adv, 
            "GEX.markers.ILC2_adv.1110.csv", 
            col.names = TRUE,
            row.names = FALSE,
            quote = F,
            sep = ",")
```


```{r fig.width=4.5, fig.height=12}
# 
DotPlot(GEX.seur, features = markers.top16[!duplicated(markers.top16$gene),"gene"],
             assay='RNA' , group.by = "seurat_clusters" )  + coord_flip()
```

```{r fig.width=12,fig.height=54}
FeaturePlot(GEX.seur, features = markers.top16$gene[1:96],
            reduction = 'umap')
```


```{r fig.width=12,fig.height=54}
VlnPlot(GEX.seur, features = markers.top16$gene[1:96],
            group.by = "seurat_clusters")
```

```{r}
GEX.seur$Anno_ILC2 <- factor(paste0("ILC2_",as.character(GEX.seur$seurat_clusters)),
                             levels = paste0("ILC2_",c(0,4,1,5,2,3)))
```



```{r fig.width=12, fig.height=12}
marker.new <- c((markers.top16 %>% filter(cluster==0))$gene,
                (markers.top16 %>% filter(cluster==4))$gene,
                (markers.top16 %>% filter(cluster==1))$gene,
                (markers.top16 %>% filter(cluster==5))$gene,
                (markers.top16 %>% filter(cluster==2))$gene,
                (markers.top16 %>% filter(cluster==3))$gene)
p.heat_top16 <- DoHeatmap(GEX.seur , group.by = "Anno_ILC2", 
             features = marker.new) +
             NoLegend() + labs(title = "ILC2_newclusters top16\n")
p.heat_top16
```

```{r fig.width=12, fig.height=12}
marker.top80 <- c((GEX.markers.ILC2_adv %>% group_by(cluster) %>% filter(avg_log2FC >0.25) %>% top_n(n = 80, wt = avg_log2FC) %>% filter(cluster==0))$gene,
                (GEX.markers.ILC2_adv %>% group_by(cluster) %>% filter(avg_log2FC >0.25) %>% top_n(n = 80, wt = avg_log2FC) %>% filter(cluster==4))$gene,
                (GEX.markers.ILC2_adv %>% group_by(cluster) %>% filter(avg_log2FC >0.25) %>% top_n(n = 80, wt = avg_log2FC) %>% filter(cluster==1))$gene,
                (GEX.markers.ILC2_adv %>% group_by(cluster) %>% filter(avg_log2FC >0.25) %>% top_n(n = 80, wt = avg_log2FC) %>% filter(cluster==5))$gene,
                (GEX.markers.ILC2_adv %>% group_by(cluster) %>% filter(avg_log2FC >0.25) %>% top_n(n = 80, wt = avg_log2FC) %>% filter(cluster==2))$gene,
                (GEX.markers.ILC2_adv %>% group_by(cluster) %>% filter(avg_log2FC >0.25) %>% top_n(n = 80, wt = avg_log2FC) %>% filter(cluster==3))$gene)
p.heat_top80 <- DoHeatmap(GEX.seur , group.by = "Anno_ILC2", 
             features = marker.top80) +
             NoLegend() + labs(title = "ILC2_newclusters top80\n")+ theme( axis.text.y = element_text( size = 4 ))
p.heat_top80
```


```{r eval=FALSE, include=FALSE}
ggsave("Doheatmap.ILC2newclusters_top16.pdf",
       plot = p.heat_top16,
       width = 12,
       height = 12)
ggsave("Doheatmap.ILC2newclusters_top80.pdf",
       plot = p.heat_top80,
       width = 12,
       height = 12)
```


## condition comparison                                  


### DEGs           


```{r message=TRUE, warning=TRUE, include=FALSE}
# find DEGs in all clusters for 'cKO vs CTL'
#Idents(GEX.seur) <- "SP.info"

names_adv <- levels(GEX.seur$Anno_ILC2)
#GEX.DEGs_adv <- list()
#for(nn in names_adv){
#  GEX.DEGs_adv[[nn]] <- FindAllMarkers(subset(GEX.seur, subset = Anno_ILC2 == nn),
#                                         only.pos = TRUE, 
#                                         min.pct = 0.1, 
#                                         logfc.threshold = 0.25,
#                                         test.use = "MAST")
#}
#for(nn in names_adv){
#  GEX.DEGs_adv[[nn]]$Anno_ILC2 <- nn
#}
Idents(GEX.seur) <- "Anno_ILC2"

GEX.DEGs_adv <- readRDS("GEX.DEGs.ILC2_adv.rds")
```

```{r eval=FALSE, include=FALSE}
# save DEG result
saveRDS(GEX.DEGs_adv, "GEX.DEGs.ILC2_adv.rds")

# save as datafrmae
GEX.DEGs_adv.df <- data.frame()
for(nn in names_adv){
  GEX.DEGs_adv.df <- rbind(GEX.DEGs_adv.df,GEX.DEGs_adv[[nn]])
}
#GEX.DEGs_adv.df
write.table(data.frame(gene=rownames(GEX.DEGs_adv.df),
                       GEX.DEGs_adv.df), "GEX.DEGs.ILC2_adv.csv", col.names = T, row.names = F, quote = F, sep = ",")

```

```{r}
lapply(GEX.DEGs_adv,function(x) x %>% group_by(cluster) %>% top_n(n = 8, wt = avg_log2FC))
```

```{r}
lapply(GEX.DEGs_adv,dim)
```

```{r message=FALSE, warning=FALSE}
vln_DEGs.adv <- list()
Idents(GEX.seur) <- "SP.info"
for(nn in names_adv){
  pp.test <- VlnPlot(subset(GEX.seur, subset = Anno_ILC2 == nn), 
               features = (GEX.DEGs_adv[[nn]] %>% group_by(cluster) %>% top_n(n = 8, wt = avg_log2FC))$gene,
               combine = F)
  title <- cowplot::ggdraw() + cowplot::draw_label(nn, fontface = 'bold', size = 9)
  for(pp in 1:length(pp.test)){
    pp.test[[pp]] <- pp.test[[pp]] + NoLegend()
  }
  vln_DEGs.adv[[nn]] <- cowplot::plot_grid(title = title,plotlist =  pp.test, ncol = 4)
}
Idents(GEX.seur) <- "Anno_ILC2"
```

##### top 8 vlnplot           

```{r echo=FALSE, fig.height=15, fig.width=8}
vln_DEGs.adv
```


### cell composition                    

#### FB.info      

```{r}
Idents(GEX.seur) <- "Anno_ILC2"
```

```{r fig.width=9.2,fig.height=3.2}
DimPlot(GEX.seur, reduction = "umap", label = F,group.by = "FB.info",
        cols = c("#05BE78","#5ECDF2","#739BDD","#B7E16F","#87C0C9","#7756FA","#9855B9","#6F9920"))+
  DimPlot(GEX.seur, reduction = "umap", label = T)
```


```{r fig.width=12,fig.height=5.2}
DimPlot(GEX.seur, group.by = "FB.info", split.by = "FB.info", ncol = 4,
        cols = c("#05BE78","#5ECDF2","#739BDD","#B7E16F","#87C0C9","#7756FA","#9855B9","#6F9920"))
```

```{r}
table(data.frame(GEX.seur$FB.info,GEX.seur$Anno_ILC2))
```

```{r fig.width=5, fig.height=3}
pheatmap::pheatmap(table(data.frame(GEX.seur$FB.info,GEX.seur$Anno_ILC2)),
                   main = "Cell Count",
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.0f")
```

```{r fig.width=5, fig.height=3}
pheatmap::pheatmap(100*rowRatio(table(data.frame(GEX.seur$FB.info,GEX.seur$Anno_ILC2))),
                   main = "Percentage of Sample count(row)",
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.2f")
```

#### SP.info        


```{r fig.width=9.2,fig.height=3.2}
DimPlot(GEX.seur, reduction = "umap", label = F,group.by = "SP.info",
        cols = c("#76797C","#0000C8","#FDB911"))+
  DimPlot(GEX.seur, reduction = "umap", label = T)
```

```{r fig.width=12,fig.height=3.6}
DimPlot(GEX.seur, group.by = "SP.info", split.by = "SP.info",cols = c("#76797C","#0000C8","#FDB911"), ncol = 3)
```

```{r}
table(data.frame(GEX.seur$SP.info,GEX.seur$Anno_ILC2))
```



```{r fig.width=5, fig.height=2.4}
pheatmap::pheatmap(table(data.frame(GEX.seur$SP.info,GEX.seur$Anno_ILC2)),
                   main = "Cell Count",
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.0f")
```

```{r fig.width=5, fig.height=2.4}
pheatmap::pheatmap(100*rowRatio(table(data.frame(GEX.seur$SP.info,GEX.seur$Anno_ILC2))),
                   main = "Percentage of Sample count(row)",
                   cluster_rows = F, cluster_cols = F, display_numbers = T, number_format = "%.2f")
```

```{r eval=FALSE, include=FALSE}
saveRDS(GEX.seur,"adv_1110.GEX.seur_ILC2.Anno.rds")
```



## topic model               

basically follow https://bitbucket.org/jerry00/mouse_small_intestine_immune_cell_atlas/src/master/script/topicModeling_PP.R     

```{r}
source("../analysis_1101/topicmodel.r")
```

### calculate topics         

```{r}
# using umap coordinates
GEX.seur@reductions[['umap']]@cell.embeddings[1:5,1:2]
```

```{r}
# to exclude ribosomal
ribo.loc <- grepl("Rpl|Rps", rownames(GEX.seur@assays[['RNA']]@counts))
head(rownames(GEX.seur@assays[['RNA']]@counts)[ribo.loc])
sum(ribo.loc)
```
```{r}
# Build topic models and generate assocaited figures 
# Recommended to build models for k = 3,4,5,6,7,8,9,10 and tolerance 0.1 (set as inputs to this function)
# each K would take hours, bigger K, longer time
# so slow, would run into three sub-scripts from 3 to 10
#for(kk in c(3,4,5,6,7,8,9,10)){
#  kkk <- kk
#  if(kk %in% c(4,6,8)){
#    kkk <- paste0(0,kk)
#  }
#  FitGoM(t(as.matrix(GEX.seur@assays[['RNA']]@counts)[!ribo.loc,]),
#         K = kk, tol = 0.1,
#         path_rda =paste0("topicmodel/test_topic.n",kkk,"_t0.1.rda"))
#}
```




























